Covariates analysis of MSBB reprocessed RNASeq data

### 2016-07-14 code/Rmd/MSSM_RNASeq_SVA_Reprocessed.Rmd
Added parallel version of num.sv and minor modifications in MSSM SVA reprocessed counts

devtools::source_url("https://raw.githubusercontent.com/chr1swallace/random-functions/master/R/ggplot-heatmap.R")

@@

# Find PC of residual gene expression and significant covariates that are highly correlated with PCs
residualSigCovars = runPCAandPlotCorrelations(RESIDUAL.GENE_EXPRESSION, 
                                              COVARIATES, 'all adjusted design(voom-normalized)',
                                              isKeyPlot=TRUE)
```
`r tmp`
### Sanity check
```{r residualSigCovars.manual, fig.width=20, fig.height=12}
residualSigCovars[["PC_res"]][[2]]$plotData
```
### Estimate surrogate variables using SVA package
```{r sva}
MODEL0 = DM1$design[,-grep('BrainRegion.Diagnosis',colnames(DM1$design))] # Get null model by removing variable of interest
MODEL1 = DM1$design

## Calculate the number of surrogate variables
NUM.SV = num.sv(VOOM.ADJUSTED.GENE_EXPRESSION$E, MODEL1, method = 'be', seed = 123456, LINPACK = TRUE, B = 10)

>>>>

devtools::source_url("https://raw.githubusercontent.com/chr1swallace/random-functions/master/R/ggplot-heatmap.R")
source('../R/num.sv.R') # Source parallel version of num.sv from local repo

@@

# Find PC of residual gene expression and significant covariates that are highly correlated with PCs
residualSigCovars = runPCAandPlotCorrelations(RESIDUAL.GENE_EXPRESSION, 
                                              COVARIATES, 'all adjusted design(voom-normalized)',
                                              isKeyPlot=TRUE)
```
### Sanity check
```{r residualSigCovars.manual, fig.width=20, fig.height=12}
residualSigCovars[["PC_res"]][[2]]$plotData
```
### Estimate surrogate variables using SVA package
```{r sva}
MODEL0 = DM1$design[,-grep('BrainRegion.Diagnosis',colnames(DM1$design))] # Get null model by removing variable of interest
MODEL1 = DM1$design

## Calculate the number of surrogate variables
NUM.SV = num.sv(VOOM.ADJUSTED.GENE_EXPRESSION$E, MODEL1, method = 'be', seed = 123456, B = 10)
